Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-11-10 neurips-20/infinite-outcomes.tex
Adding writeup of Ioffe proof

\begin{condition}[\cite[Lemma 4.5]{dupacova1988asymptotic}]
	$f$ is LSC and Lipschitz.
\end{condition}

@@

\section{Result}
\begin{corollary}[\cite{rockafellar1982interchange,ioffe1969minimization}]
	Suppose $f$ is an $\A$-normal convex integrand such that $F(x) < \infty$ whenever $x \in \dom(f(\cdot,y))$ almost surely, where $F(x) = \E_p f(x,Y)$.

>>>>

\begin{condition}[\cite{dupacova1988asymptotic} Lemma 4.5]
	$f$ is LSC and Lipschitz.
\end{condition}

@@

Worth noting the commentary around~\cite[Equation 7]{ioffe1969minimization}.

\section{The OG proof, with our assumptions}
Consider the integral $I_f(u) = \int f(u,y) d(py)$ given the finite $\sigma$-algebra $(\Y, \A, p)$.

\cite{ioffe1969minimization} assumes $f$ is $\A$-measurable, convex, and closed (i.e. lower semicontinuous) in $u$.
We assume that $\dom f = \reals^d$ and that for all $u \in \reals^d,y \in \Y$, $f(u,y) < \infty$, which, with convexity implies the latter two conditions above.

In~\cite[Equation 7]{ioffe1969minimization}, the authors show 
\begin{equation}
\partial \E_p f(u,Y) = \E_p \partial f(u,Y) + \partial \delta_{\effdom \E_p f(u,Y)}~.~
\end{equation}

Given our assumptions that $\E_p f(u,Y) < \infty$ for all $u$ (and $p \in \P$), we have $\Lambda(u) := \partial \delta_{\effdom \E_p f(u,Y)} = \{\vec 0\}$, reducing the equation to the interchange of expectation and subdifferentiation.
For brevity, we write $\E_p f(u,Y) = F(u)$.

Their proof goes as follows:
First, $\E_p \partial f(u,Y) \subseteq \partial F(u)$ for all $u \in \reals^d$ follows immediately \jessie{according to them... I don't see why} from the definition \jessie{of integration}, which implies the inclusion $\E_p \partial f(u,Y) + \Lambda(u) \subseteq \partial F(u)$ since $\vec 0 \in \Lambda(u)$.

Therefore, it is just left to prove $\partial F(u) \subseteq \E_p \partial f(u,Y) + \Lambda(u)$.

The proof proceeds by contradiction; if $\partial F(u) \neq \emptyset$ we can assume there is a $y_0 \in \partial F(u)$ so that $y_0 \not \in \E_p \partial f(u,Y) + \Lambda(u) = \E_p \partial f(u,Y)$.
Therefore, by some of their Lemmas~\cite[Lemmas 1, 2]{ioffe1969minimization}, we have $\E_p \partial f(u,Y)$ is not empty, convex, and closed, and can therefore be strictly separated from $y_0$.
Therefore, for some $z'$, we have $\langle z', y_0 \rangle \geq \langle z', y \rangle + \epsilon$ for some $\epsilon > 0$ and $y \in \E_p \partial f(u,Y)$

Now define $\psi(z) := \sup_{y \in \E_p \partial f(u,Y)} \langle z,y \rangle$, which is a supporting function of $\E_p f(u,Y)$; it is also convex and closed.

Moreover, $\dom \psi = \reals$, and we have $\psi(z') \leq \langle z', y_0 \rangle - \epsilon$.
However, according to their Lemma 1, there exists a $y \in \E_p \partial f(u,Y)$ so that $\langle z', y \rangle = F'(u,z') = \langle z', y \rangle \leq \psi(z') < \langle z', y_0 \rangle$.\footnote{$F'(u,z')$ is the directional derivative of $F$ at $u$ in the $z'$ direction.}

This would imply $y_0 \not \in \partial F(u)$, contradicting the initial assumption.
Thus, we have $\partial \E_p f(u,Y) = \E_p \partial f(u,Y)$.

Proof picture in Figure~\ref{fig:ioffeproofpic}.
\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{tikz/ioffeproofpic}
	\caption[Picture understanding proof of Ioffe result]{}
	\label{fig:ioffeproofpic}
\end{figure}

\section{Result}
\begin{corollary}[\cite{rockafellar1982interchange}]
	Suppose $f$ is an $\A$-normal convex integrand such that $F(x) < \infty$ whenever $x \in \dom(f(\cdot,y))$ almost surely, where $F(x) = \E_p f(x,Y)$.
